Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 Moltres.tex
explortation->exploration, thanks @lindsayad
This removes the overstatement about unmatched fidelity

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations in anywhere
from one to three dimensions and can be deployed on an arbitrary number of
processing units. Through its computing power, Moltres is devoted to previously
unmatched fidelity in coupled neutronics and thermal hydraulics \gls{MSR}
simulation.

@@

Finally, the authors would like to thank Matthew Turk and the Data Explortation 
Lab for co-supporting Dr. Lindsay during his postdoctoral appointment.

>>>>

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations in anywhere
from one to three dimensions and can be deployed on an arbitrary number of
processing units.

@@

Finally, the authors would like to thank Matthew Turk and the Data Exploration 
Lab for co-supporting Dr. Lindsay during his postdoctoral appointment.
